### 2020-12-20 paper/calibration_and_estimation.tex
Update figures and pseudocode.

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/assortative_matching_probability_example.png}
    \caption{Distribution of random non-work contacts by age of participants}
    \label{fig:assortativeness}
\end{figure}

Figure~\ref{fig:assortativeness} shows that overall contacts within age groups or age
groups that are closer to each other are more frequent.

>>>>

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/assortative_matching_probability_example.png}
    \caption{Distribution of random non-work contacts by age of participants.}
    \label{fig:assortativeness}
    \figurenotes{
        The figure shows the distribution of random non-work contacts by age groups. A
        row shows the share of contacts a certain age group has with all other age
        groups. Higher values are colored in darker red tones. The diagonal represents
        the share of contacts with individuals from the same age group.
    }
\end{figure}

Figure~\ref{fig:assortativeness} shows that assortativeness by age is especially strong
for children and younger adults. For older people, the pattern becomes more dispersed
around their own age group, but within-age-group contacts are still the most common
contacts.

### 2020-12-20 paper/model/matching.tex
Enforced 88 character limit.
Update figures and pseudocode.

%%% ToDo: Get syntax highlighting for the pseudo code. Try out different languages.

\begin{lstlisting}
while unmatched contacts remain:
    model, id = draw contact model and individual
    for contact in remaining_contacts[id, model]:
        draw group of other person
        draw other person from that group
        determine if id infects other or vice versa
        remaining_contacts[id, model] -= 1
        remaining_contacts[other, model] -= 1
\end{lstlisting}

We first randomly draw a contact type and individual. For each contact oth the drawn contact type that person has, we first draw the group of the other person (first stage). Next, we calculate the probability to be drawn for each member of the group, based on the number of remaining contacts. I.e. people who have more remaining contacts are drawn with a higher probability. This has to be re-calculated each time because with each matched contact, the number of remaining contacts changes. We then draw the other individual, determine whether an infection takes place and if so update the health states of the newly infected person. Finally, we reduce the number of remaining contacts of the two matched individuals by one.

>>>>

\begin{listing}
    \label{code:matching}
    \begin{minted}{python}
        while are_unmatched_contacts_left:

            contact_type, i = draw_contact_type_and_individual()

            for _ in remaining_contacts[i, contact_type]:

                group_j = draw_group_of_other_person()
                j = draw_other_person_from_that_group(group_j)

                if infection_takes_places(i, j):
                    # Update health statuses.

                remaining_contacts[i, contact_type] -= 1
                remaining_contacts[j, contact_type] -= 1
    \end{minted}
    \caption{Pseudo-code for the matching algorithm of non-recurrent contacts.}
\end{listing}

We first randomly draw a contact type and individual. For each contact of the drawn
contact type that person has, we first draw the group of the other person (first stage).
Next, we calculate the probability to be drawn for each member of the group, based on
the number of remaining contacts. I.e. people who have more remaining contacts are drawn
with a higher probability. This has to be re-calculated each time because with each
matched contact, the number of remaining contacts changes. We then draw the other
individual, determine whether an infection takes place and if so update the health
states of the newly infected person. Finally, we reduce the number of remaining contacts
of the two matched individuals by one.

### 2020-12-20 paper/model_validation.tex
Enforced 88 character limit.
Update figures and pseudocode.

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/goodness_of_fit_by_age_group}
    \caption{Actual vs. simulated infection and fatality rates}
    \label{fig:goodness_of_fit}
\end{figure}

@@

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/out_of_sample_validation}
    \caption{Projected effect of the lockdown-light}
    \label{fig:out-of-sample-fit}
\end{figure}

>>>>

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/goodness_of_fit_by_age_group}
    \caption{Reported vs. simulated weekly incidence rates of infections.}
    \label{fig:goodness_of_fit}
    \figurenotes{
        The figure shows the weekly incidence rates per 100,000 people for the reported
        (red line) versus the simulated infections rates (blue line) for age groups
        available in the data provided by the Robert-Koch Institut.
    }
\end{figure}

@@

\begin{figure}[!tp]
    \centering
    \includegraphics[width=\textwidth]{../figures/out_of_sample_validation}
    \caption{Predicted effect of the "Lockdown Light" on infection rates.}
    \label{fig:out-of-sample-fit}
    \figurenotes{
        For the time period until the beginning of November, the figure shows the weekly
        incidence rates of infections per 100,000 people from reported (black) versus
        simulated (blue) data. With the start of November, the projections of the three
        scenarios, optimistic (blue), neutral (red), and pessimistic (mint green), are
        shown until the beginning of the Christmas holidays. The actual incidence rates
        (black) are reported until the 24th November.
    }
\end{figure}
